---
title: "PHOSP clustering"
author: "PHOSP-COVID collaborative"
output:
  word_document:
    toc: yes
    toc_depth: '3'
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
if (knitr::is_html_output()){
  knitr::opts_chunk$set(echo = TRUE,
                        warning = FALSE,
                        message = FALSE)
} else {
  knitr::opts_chunk$set(echo = FALSE,
                        warning = FALSE,
                        message = FALSE)
}

library(finalfit)
library(knitr)
library(tidyverse)
library(rmarkdown)
library(cluster)
library(ggh4x)

summary_factorlist <- purrr::partial(finalfit::summary_factorlist, na_to_prop = FALSE)
```

```{r}
# For exploration 
library(readr) # loaded with tidyverse anyway
datadir = "/home/common/phosp/raw/"
timestamp = "2021-03-12_1624"
phosp   = read_rds(paste0(datadir, "phosp_", timestamp, ".rds"))
lastrun = Sys.time()
source("02_functions.R")
source("03_prep.R")
# source("04_clustering.R")
source("05_kco.R")
```

### Tier 2 cohort before 30 Nov 2020 with < 240 days follow-up 

```{r}
# Filter at 240 days follow up. 
study_id_240 = phosp %>% 
  group_by(study_id) %>% 
  fill(crf1a_date_dis, crf3a_visit_date, .direction = "downup") %>% 
  select(study_id, crf1a_date_dis, crf3a_visit_date) %>% 
  distinct(study_id, .keep_all = TRUE) %>% 
  mutate(discharge2review = (crf3a_visit_date - crf1a_date_dis) %>% as.numeric()) %>% 
  filter(discharge2review <= 240 | is.na(discharge2review)) %>% 
  pull(study_id)
```

```{r}
keep = phosp_hosp %>% 
  filter(tier == 2) %>% 
  filter(study_id %in% study_id_before_end_nov) %>%
  filter(study_id %in% study_id_240) %>% 
  drop_na(crf1a_resp_support_4levels) %>% 
  filter(!is.na(crf1a_sex)) %>% 
  filter(study_id != "28-31") %>% # Temp remove as no 3 m data coming through
  pull(study_id)

phosp_hosp = phosp_hosp %>% 
  filter(study_id %in% keep)

phosp_3m = phosp_3m %>% 
  left_join(phosp_hosp %>% select(study_id, crf1a_resp_support_4levels)) %>% 
  filter(study_id %in% keep)

phosp = phosp %>% 
  filter(study_id %in% keep)

phosp_wt = phosp_wt %>% 
  filter(study_id %in% keep)
```

```{r}
# Any joins can be temporarily done here, then moved to cleaning. 
phosp_hosp = phosp_hosp %>% 
  left_join(phosp %>% 
              filter(redcap_event_name == "3 Months (1st Research Visit)") %>% 
              select(study_id, crf3a_bmi, crf3a_bmi_2levels, crf3a_bmi_5levels) %>% 
              drop_na(crf3a_bmi)
  )
```

```{r}
# Temp variable changes / collapses

## Pull psq_recovered from 6 week data if missing at 3 months
phosp_hosp = phosp_hosp %>% 
  left_join(phosp_3m %>% select(study_id, psq_recovered, eq5d5l_summary_delta, discharge_to_3m_review)) %>%
  left_join(phosp_6w %>% select(study_id, 
                                psq_recovered_6w = psq_recovered,
                                eq5d5l_summary_delta_6w = eq5d5l_summary_delta)) %>% 
  mutate(
    psq_recovered = case_when(
      is.na(psq_recovered) & !is.na(psq_recovered_6w) ~ psq_recovered_6w,
      TRUE ~ psq_recovered
    ) %>% fct_recode("No" = "Not sure") %>% 
      fct_relevel("No"),
    
    eq5d5l_summary_delta = case_when(
      is.na(eq5d5l_summary_delta) & !is.na(eq5d5l_summary_delta_6w) ~ eq5d5l_summary_delta_6w,
      TRUE ~ eq5d5l_summary_delta)
  ) %>% 
  ff_relabel_df(phosp_hosp)
```

```{r}
# Smoking
phosp_smoking = phosp_3m %>% 
  select(study_id, patient_sq_n) %>% 
  left_join(phosp_6w %>% select(study_id, patient_sq_n_6w = patient_sq_n)) %>% 
  mutate(patient_sq_n= case_when(
    is.na(patient_sq_n) & !is.na(patient_sq_n_6w) ~ patient_sq_n_6w,
    TRUE ~ patient_sq_n
  ) %>% 
    ff_label("Smoking")
  ) %>% 
  select(study_id, patient_sq_n)

phosp_hosp = phosp_hosp %>% 
  left_join(phosp_smoking) %>% 
  mutate(patient_sq_n = ff_label(patient_sq_n, "Smoking"))
```


## Number of patients in clustering

```{r}
explanatory_hrqol = c(
  "gad7_summary",
  "phq9_summary",
  "pcl5_summary",
  "dyspnoea12_summary",
  "facit_item_total",
  "sppb_score",
  "mocal_total"
)

phosp_3m %>% 
  select(explanatory_hrqol) %>%
  missing_glimpse() %>% 
  mytable()

phosp_3m %>% 
  select(explanatory_hrqol) %>%
  drop_na() %>% 
  count(name = "Complete cases") 
```


```{r fig.height=6, fig.width=8}
# Normalise
library(recipes)
set.seed(1234)
clara_result = phosp_3m %>% 
  select(study_id, explanatory_hrqol) %>% 
  drop_na() %T>% 
  {data_in <<- .} %>% 
  select(-study_id) %>% 
  recipe(~ .) %>% 
  step_normalize(all_numeric()) %>% 
  prep() %>% 
  juice() %>% 
  mutate(across(c(mocal_total, sppb_score), ~ . * -1)) %>%     # Reverse scale for these
  clara(4, samples = 50,  pamLike = TRUE, metric = "euclidean")
clara_result
# plot(clara_result)

clara_result$medoids %>% 
  as_tibble() %>% 
  mutate(cluster = (1:max(row_number()) %>% factor())) %>% 
  gather("key", "value", -cluster) %>% 
  mutate(key = factor(key) %>% 
           fct_recode(
             "Anxiety (GAD7)" = "gad7_summary",
             "Depression (PHQ7)" = "phq9_summary",
             "PTSD (PCL5)" = "pcl5_summary",
             "Breathlessness (Dyspnoea-12)" = "dyspnoea12_summary",
             "Fatigue (FACIT)" = "facit_item_total",
             "Physical Performance (SPPB)" = "sppb_score",
             "Cognition (MoCA)" = "mocal_total") %>% 
           fct_relevel(
             "Anxiety (GAD7)",
             "Depression (PHQ7)",
             "PTSD (PCL5)",
             "Breathlessness (Dyspnoea-12)",
             "Fatigue (FACIT)",
             "Physical Performance (SPPB)",
             "Cognition (MoCA)"
           )
  ) %>% 
  
  ggplot_lancet(aes(x = fct_rev(key), y = value, colour = cluster, group = cluster)) +
  geom_line(stat = "identity") +
  geom_hline(yintercept = 0, linetype = 2) +
  coord_flip() +
  scale_colour_brewer("Cluster", palette = "Set1") + 
  labs(x = "", y = "Z-score (high is more deficit)") +
  ggtitle("Cluster centres (medoids) for symptom questionnaires",
          "Normalised scale (z-scores)")
```

```{r}
phosp_cluster = data_in %>% 
  mutate(cluster = clara_result$clustering %>% 
           factor(levels = c(1, 2, 3, 4),
                  labels = c(
                    "1: Very severe mental/physical impairment",
                    "2: Severe mental/physical impairment",
                    "3: Moderate mental/physical impairment + poor cognition",
                    "4: Mild impairment"),
           )) %>% 
  select(study_id, cluster)

```

## Cluster medoids (z-scores)  

```{r}
clara_result$medoids %>%
  as_tibble() %>% 
  mutate(
    Cluster = 1:4
  ) %>% 
  rename(
    "Anxiety (GAD7)" = "gad7_summary",
    "Depression (PHQ7)" = "phq9_summary",
    "PTSD (PCL5)" = "pcl5_summary",
    "Breathlessness (Dyspnoea-12)" = "dyspnoea12_summary",
    "Fatigue (FACIT)" = "facit_item_total",
    "Physical Performance (SPPB)" = "sppb_score",
    "Cognition (MoCA)" = "mocal_total"
  ) %>% 
  relocate("Cluster") %>% 
  mytable()
```

## Cluster characteristics  

```{r}
clara_result$clusinfo %>%
  as_tibble() %>% 
  mutate(
    Cluster = 1:4
  ) %>% 
  rename(
    "Size" = "size",
    "Maximal dissimilarity" = "max_diss",
    "Average dissimilarity" = "av_diss",
    "Isolation" = "isolation"
  ) %>% 
  relocate("Cluster") %>% 
  mytable()
```



```{r moca, fig.height=6, fig.width=8}
explanatory_hrqol = c(
  "gad7_summary",
  "phq9_summary",
  "pcl5_summary",
  "dyspnoea12_summary",
  "facit_item_total",
  "sppb_score",
  "mocal_total"
)  

scales_y = list(
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_reverse()
)

scales_x = list(
  scale_x_reverse(), 
  scale_x_reverse(), 
  scale_x_reverse(), 
  scale_x_reverse(), 
  scale_x_reverse(), 
  scale_x_reverse()
)

# MOCA
phosp_3m %>% 
  left_join(phosp_cluster) %>% 
  select(cluster, explanatory_hrqol) %>% 
  drop_na() %>% 
  gather("key", "value", -c(cluster, mocal_total)) %>% 
  mutate(
    key = factor(key) %>% 
      fct_recode(
        "Anxiety (GAD7)" = "gad7_summary",
        "Depression (PHQ7)" = "phq9_summary",
        "PTSD (PCL5)" = "pcl5_summary",
        "Breathlessness (Dyspnoea-12)" = "dyspnoea12_summary",
        "Fatigue (FACIT)" = "facit_item_total",
        "Physical Performance (SPPB)" = "sppb_score"
      )
  ) %>% 
  ggplot_lancet(aes(mocal_total, value, colour = cluster)) +
  geom_jitter(alpha = 0.5) + 
  xlim(c(10, NA)) +
  # scale_x_reverse() +
  scale_colour_brewer(palette = "Set1") + 
  labs(x = "Cognition (MoCA)", colour = "") +
  facet_wrap(. ~ key, scale = "free_y") +
  facetted_pos_scales(y = scales_y, x = scales_x) + 
  theme(
    legend.position = c(1, 1.17)
  ) +
  guides(colour = guide_legend(title.position = "top",
                               nrow = 2)) + 
  ggtitle("",
          "")
# PDF 11 x 7
```


```{r gad7, fig.height=6, fig.width=8}
# GAD7
scales = list(
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_reverse(),
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_reverse()
)

phosp_3m %>% 
  left_join(phosp_cluster) %>% 
  select(cluster, explanatory_hrqol) %>% 
  drop_na() %>% 
  gather("key", "value", -c(cluster, gad7_summary)) %>% 
  mutate(
    key = factor(key) %>% 
      fct_recode(
        #"Anxiety (GAD7)" = "gad7_summary",
        "Depression (PHQ7)" = "phq9_summary",
        "PTSD (PCL5)" = "pcl5_summary",
        "Breathlessness (Dyspnoea-12)" = "dyspnoea12_summary",
        "Fatigue (FACIT)" = "facit_item_total",
        "Physical Performance (SPPB)" = "sppb_score",
        "Cognition (MoCA)" = "mocal_total"
      )
  ) %>% 
  ggplot_lancet(aes(gad7_summary, value, colour = cluster)) +
  geom_jitter(alpha = 0.5) + 
  scale_colour_brewer(palette = "Set1") + 
  labs(x = "Anxiety (GAD7)", colour = "") +
  facet_wrap(. ~ key, scale = "free_y") +
  facetted_pos_scales(y = scales) + 
  theme(
    legend.position = c(1, 1.17)
  ) +
  guides(colour = guide_legend(title.position = "top",
                               nrow = 2)) + 
  ggtitle("Symptom instruments by GAD7",
          " ")
```


```{r phq7, fig.height=6, fig.width=8}
# PHQ7
scales = list(
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_reverse(),
  scale_y_continuous(),
  scale_y_reverse()
)

phosp_3m %>% 
  left_join(phosp_cluster) %>% 
  select(cluster, explanatory_hrqol) %>% 
  drop_na() %>% 
  gather("key", "value", -c(cluster, phq9_summary)) %>% 
  mutate(
    key = factor(key) %>% 
      fct_recode(
        "Anxiety (GAD7)" = "gad7_summary",
        # "Depression (PHQ7)" = "phq9_summary",
        "PTSD (PCL5)" = "pcl5_summary",
        "Breathlessness (Dyspnoea-12)" = "dyspnoea12_summary",
        "Fatigue (FACIT)" = "facit_item_total",
        "Physical Performance (SPPB)" = "sppb_score",
        "Cognition (MoCA)" = "mocal_total"
      )
  ) %>% 
  ggplot_lancet(aes(phq9_summary, value, colour = cluster)) +
  geom_jitter(alpha = 0.5) + 
  scale_colour_brewer(palette = "Set1") + 
  labs(x = "Depression (PHQ7)" , colour = "") +
  facet_wrap(. ~ key, scale = "free_y") +
  facetted_pos_scales(y = scales) + 
  theme(
    legend.position = c(1, 1.17)
  ) +
  guides(colour = guide_legend(title.position = "top",
                               nrow = 2)) + 
  ggtitle("Symptom instruments by PHQ7",
          " ")
```



```{r pcl5, fig.height=6, fig.width=8}
# PCL5
scales = list(
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_reverse(),
  scale_y_continuous(),
  scale_y_reverse()
)

phosp_3m %>% 
  left_join(phosp_cluster) %>% 
  select(cluster, explanatory_hrqol) %>% 
  drop_na() %>% 
  gather("key", "value", -c(cluster, pcl5_summary)) %>% 
  mutate(
    key = factor(key) %>% 
      fct_recode(
        "Anxiety (GAD7)" = "gad7_summary",
        "Depression (PHQ7)" = "phq9_summary",
        # "PTSD (PCL5)" = "pcl5_summary",
        "Breathlessness (Dyspnoea-12)" = "dyspnoea12_summary",
        "Fatigue (FACIT)" = "facit_item_total",
        "Physical Performance (SPPB)" = "sppb_score",
        "Cognition (MoCA)" = "mocal_total"
      )
  ) %>% 
  ggplot_lancet(aes(pcl5_summary, value, colour = cluster)) +
  geom_jitter(alpha = 0.5) + 
  scale_colour_brewer(palette = "Set1") + 
  labs(x = "PTSD (PCL5)", colour = "") +
  facet_wrap(. ~ key, scale = "free_y") +
  facetted_pos_scales(y = scales) + 
  theme(
    legend.position = c(1, 1.17)
  ) +
  guides(colour = guide_legend(title.position = "top",
                               nrow = 2)) + 
  ggtitle("Symptom instruments by PCL5",
          " ")
```

```{r dys, fig.height=6, fig.width=8}
# DYS
scales = list(
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_reverse(),
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_reverse()
)


phosp_3m %>% 
  left_join(phosp_cluster) %>% 
  select(cluster, explanatory_hrqol) %>% 
  drop_na() %>% 
  gather("key", "value", -c(cluster, dyspnoea12_summary)) %>% 
  mutate(
    key = factor(key) %>% 
      fct_recode(
        "Anxiety (GAD7)" = "gad7_summary",
        "Depression (PHQ7)" = "phq9_summary",
        "PTSD (PCL5)" = "pcl5_summary",
        # "Breathlessness (Dyspnoea-12)" = "dyspnoea12_summary",
        "Fatigue (FACIT)" = "facit_item_total",
        "Physical Performance (SPPB)" = "sppb_score",
        "Cognition (MoCA)" = "mocal_total"
      )
  ) %>% 
  ggplot_lancet(aes(dyspnoea12_summary, value, colour = cluster)) +
  geom_jitter(alpha = 0.5) + 
  scale_colour_brewer(palette = "Set1") + 
  labs(x = "Breathlessness (Dyspnoea-12)", colour = "") +
  facet_wrap(. ~ key, scale = "free_y") +
  facetted_pos_scales(y = scales) + 
  theme(
    legend.position = c(1, 1.17)
  ) +
  guides(colour = guide_legend(title.position = "top",
                               nrow = 2)) + 
  ggtitle("Symptom instruments by Dyspnoea-12",
          " ")
```

```{r facit, fig.height=6, fig.width=8}
# FACIT
scales = list(
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_reverse(),
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_reverse()
)



phosp_3m %>% 
  left_join(phosp_cluster) %>% 
  select(cluster, explanatory_hrqol) %>% 
  drop_na() %>% 
  gather("key", "value", -c(cluster, facit_item_total)) %>% 
  mutate(
    key = factor(key) %>% 
      fct_recode(
        "Anxiety (GAD7)" = "gad7_summary",
        "Depression (PHQ7)" = "phq9_summary",
        "PTSD (PCL5)" = "pcl5_summary",
        "Breathlessness (Dyspnoea-12)" = "dyspnoea12_summary",
        #"Fatigue (FACIT)" = "facit_item_total",
        "Physical Performance (SPPB)" = "sppb_score",
        "Cognition (MoCA)" = "mocal_total"
      )
  ) %>% 
  ggplot_lancet(aes(facit_item_total, value, colour = cluster)) +
  geom_jitter(alpha = 0.5) + 
  scale_colour_brewer(palette = "Set1") + 
  labs(x = "Fatigue (FACIT)", colour = "") +
  facet_wrap(. ~ key, scale = "free_y") +
  facetted_pos_scales(y = scales) + 
  theme(
    legend.position = c(1, 1.17)
  ) +
  guides(colour = guide_legend(title.position = "top",
                               nrow = 2)) + 
  ggtitle("Symptom instruments by FACIT",
          " ")
```

```{r sppb, fig.height=6, fig.width=8}
# SPPB
scales_y = list(
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_reverse(),
  scale_y_continuous(),
  scale_y_continuous()
)

scales_x = list(
  scale_x_reverse(), 
  scale_x_reverse(), 
  scale_x_reverse(), 
  scale_x_reverse(), 
  scale_x_reverse(), 
  scale_x_reverse()
)


phosp_3m %>% 
  left_join(phosp_cluster) %>% 
  select(cluster, explanatory_hrqol) %>% 
  drop_na() %>% 
  gather("key", "value", -c(cluster, sppb_score)) %>% 
  mutate(
    key = factor(key) %>% 
      fct_recode(
        "Anxiety (GAD7)" = "gad7_summary",
        "Depression (PHQ7)" = "phq9_summary",
        "PTSD (PCL5)" = "pcl5_summary",
        "Breathlessness (Dyspnoea-12)" = "dyspnoea12_summary",
        "Fatigue (FACIT)" = "facit_item_total",
        # "Physical Performance (SPPB)" = "sppb_score",
        "Cognition (MoCA)" = "mocal_total"
      )
  ) %>% 
  ggplot_lancet(aes(sppb_score, value, colour = cluster)) +
  geom_jitter(alpha = 0.5) + 
  #scale_x_reverse() +
  scale_colour_brewer(palette = "Set1") + 
  labs(x = "Physical Performance (SPPB)", colour = "") +
  facet_wrap(. ~ key, scale = "free_y") +
  facetted_pos_scales(x = scales_x, y = scales_y) + 
  theme(
    legend.position = c(1, 1.17)
  ) +
  guides(colour = guide_legend(title.position = "top",
                               nrow = 2)) + 
  ggtitle("Symptom instruments by SPPB",
          " ")
```

## Table 1: Clusters by patient characteristics

```{r}
explanatory = c("swab_pcr_result", 
                "discharge_to_3m_review",
                "age_admission", 
                "crf1a_sex", 
                "crf1b_eth_5levels", 
                "imd_quintile",
                "crf3a_bmi",
                "crf3a_bmi_2levels",
                "crf3a_bmi_5levels", 
                
                "patient_sq_n",
                
                # Comorbidities
                "no_comorbid",
                "crf1a_com_card", "crf1a_com_neupsy",
                "crf1a_com_res", "crf1a_com_rheu",
                "crf1a_com_gast", "crf1a_com_mer", 
                "crf1a_com_mh", "crf1a_com_diab",
                "crf1a_com_id",
                
                "crf1a_admission_duration",
                
                "crf1a_resp_support_4levels",
                
                "crf1a_treat_ss", "crf1a_treat_at", "crf1a_treat_tdac")

dependent = "cluster"
```


### Row proportions
```{r}
phosp_hosp %>% 
  left_join(phosp_cluster) %>% 
  summary_factorlist(dependent,  explanatory, 
                     na_include = TRUE, p = TRUE,
                     add_col_totals = TRUE, column = FALSE, cont_nonpara = c(2, 4:20),
                     total_col = TRUE) %>% 
  mytable()
```


### Column proportions
```{r}
phosp_hosp %>% 
  left_join(phosp_cluster) %>% 
  summary_factorlist(dependent,  explanatory, 
                     na_include = TRUE, p = TRUE, cont_nonpara = c(2, 4:20),
                     add_col_totals = TRUE, column = TRUE,
                     total_col = TRUE) %>% 
  mytable()
```



## Table 2: Clusters by HRQoL

```{r}
explanatory_differences = c("psq_recovered",
                            "eq5d5l_summary_pre",
                            "eq5d5l_summary",
                            # Pull delta_change names
                            phosp %>% 
                              select(matches("eq5d5l_q.*_delta_change")
                              ) %>% 
                              names(),
                            "eq5d5l_utility_index_pre",
                            "eq5d5l_utility_index",
                            "eq5d5l_utility_index_delta",
                            
                            "patient_sq_l_t_disability",
                            "patient_sq_l_t__new_disability")
```

### Row proportions
```{r}
phosp_3m %>% 
  left_join(phosp_cluster) %>% 
  summary_factorlist(dependent,  explanatory_differences,
                     na_include = TRUE, column = FALSE,
                     add_col_totals = TRUE, digits = c(2, 2, 3, 1),
                     total_col = TRUE, p = TRUE) %>% 
  mytable()

```

### Column proportions

```{r}
phosp_3m %>% 
  left_join(phosp_cluster) %>% 
  summary_factorlist(dependent,  explanatory_differences,
                     na_include = TRUE, column = TRUE,
                     add_col_totals = TRUE, digits = c(2, 2, 3, 1),
                     total_col = TRUE, p = TRUE) %>% 
  mytable()

```

## Table 3

```{r}
phosp_wt_table = phosp_wt %>% 
  filter(wt_type == "Incremental shuttle walk test (ISWT) Modified 15 level") %>% 
  filter(wt_visit == "3 months") %>% 
  drop_na(wt_distance) %>% 
  mutate(wt_iswt_predicted_perc = replace_na(wt_iswt_predicted_perc, 0)) %>% # to deal with max returning inf
  group_by(study_id) %>%  # More than one test per patient
  mutate(value_max = if_else(row_number() == which.max(wt_iswt_predicted_perc), TRUE, FALSE)) %>% 
  filter(value_max) %>% 
  select(study_id, wt_distance, wt_iswt_predicted_perc) %>% 
  as.data.frame() %>% 
  ff_relabel_df(phosp_wt)

phosp_pft_table = phosp %>% 
  filter(redcap_event_name== "3 Months (1st Research Visit)") %>% 
  filter(redcap_repeat_instrument == "Pulmonary Functional Tests") %>% 
  filter(pft_spm_done == "Yes") %>% 
  select(study_id, starts_with("pft_")) %>% 
  drop_na(pft_fev1) %>% 
  group_by(study_id) %>% 
  mutate(value_max = if_else(row_number() == which.max(pft_fev1), TRUE, FALSE)) %>% 
  filter(value_max) %>% 
  select("pft_fev1_perc_pred",
         "pft_fev1",
         "pft_fev1_perc_pred_80",
         "pft_fvc_perc_pred",
         "pft_fvc",
         "pft_fvc_perc_pred_80",
         "pft_fev1_fvc_70") %>% 
  as.data.frame() %>% 
  ff_relabel_df(phosp)

# Do kco and tlco extraction and percentage normal separately. 
phosp_kco_table = phosp %>% 
  filter(redcap_event_name== "3 Months (1st Research Visit)") %>% 
  filter(redcap_repeat_instrument == "Pulmonary Functional Tests") %>% 
  filter(pft_spm_done == "Yes") %>% 
  select(study_id, pft_tlco, pft_kco) %>% 
  drop_na(pft_kco) %>% 
  left_join(phosp_kco %>% select(study_id, tlcoM_SI_pred, kcoM_SI_pred)) %>% 
  mutate(
    pft_tlco_pred = (100 * pft_tlco / tlcoM_SI_pred) %>% ff_label("TLCO % predicted"),
    pft_kco_pred = (100 * pft_kco / kcoM_SI_pred) %>% ff_label("KCO % predicted"),
    
    pft_tlco_pred_80 = case_when(
      pft_tlco_pred < 80 ~ "Yes",
      pft_tlco_pred >= 80 ~ "No",
    ) %>% 
      ff_label("TLCO predicted <80%"),
    
    pft_kco_pred_80 = case_when(
      pft_kco_pred < 80 ~ "Yes",
      pft_kco_pred >= 80 ~ "No",
    ) %>% 
      ff_label("KCO predicted <80%"),
    
  ) %>% 
  ff_relabel_df(phosp)

phosp_pft_table = phosp_pft_table %>% 
  left_join(phosp_kco_table)
```


```{r}
phosp_bloods_table = phosp %>% 
  filter(redcap_event_name== "3 Months (1st Research Visit)") %>% 
  filter(redcap_repeat_instrument == "Laboratory Results Collection Log - Routine blood tests") %>% 
  group_by(study_id) %>% 
  summarise(
    # This needs to summarise over multiple blood tests per visit. 
    # Take max values and yes over no. 
    # Convoluted by necessity. 
    # note case_when doesn't currently work with any. Known issue Feb 21
    bnp_result = ifelse(all(is.na(bnp_result)), NA, max(bnp_result, na.rm = TRUE)),
    pnbnp_result = ifelse(all(is.na(pnbnp_result)), NA, max(pnbnp_result, na.rm = TRUE)),
    bnp_summary = ifelse(any(bnp_summary == "Yes", na.rm = TRUE), "Yes", 
                         ifelse(any(bnp_summary == "No", na.rm = TRUE), "No", 
                                NA)),
    
    hba1c_result = ifelse(all(is.na(hba1c_result)), NA, max(hba1c_result, na.rm = TRUE)),
    hba1c_summary = ifelse(any(hba1c_summary == "Yes", na.rm = TRUE), "Yes", 
                           ifelse(any(hba1c_summary == "No", na.rm = TRUE), "No", 
                                  NA)),
    
    egfr_result = ifelse(all(is.na(egfr_result)), NA, max(egfr_result, na.rm = TRUE)),
    egfr_summary = ifelse(any(egfr_summary == "Yes", na.rm = TRUE), "Yes", 
                          ifelse(any(egfr_summary == "No", na.rm = TRUE), "No", 
                                 NA)),
    
    ddi_result = ifelse(all(is.na(ddi_result)), NA, max(ddi_result, na.rm = TRUE)),
    ddi_summary = ifelse(any(ddi_summary == "Yes", na.rm = TRUE), "Yes", 
                         ifelse(any(ddi_summary == "No", na.rm = TRUE), "No", 
                                NA)),
    
    crp_result = ifelse(all(is.na(crp_result )), NA, max(crp_result , na.rm = TRUE)),
    crp_summary = ifelse(any(crp_summary  == "Yes", na.rm = TRUE), "Yes", 
                         ifelse(any(crp_summary == "No", na.rm = TRUE), "No", 
                                NA)),
  ) %>% 
  ff_relabel_df(phosp)

explanatory_hrqol = c(
  "symptom_any",
  "symptom_count",
  "gad7_summary_2levels",
  "gad7_summary",
  "phq9_summary_2levels",
  "phq9_summary",
  "pcl5_summary_2levels",
  "pcl5_summary",
  "dyspnoea12_summary",
  "facit_item_total",
  "bpi_severity_summary",
  "bpi_interference_summary",
  "sppb_score",
  "sppb_score_summary",
  "wt_distance",
  "wt_iswt_predicted_perc",
  "rcf_score_summary",
  "rcf_score",
  "mocal_total_summary",
  "mocal_total",
  "mocal_total_corrected",  
  "mocal_total_corrected_summary", 
  "pft_fev1_perc_pred", 
  "pft_fev1_perc_pred_80",
  "pft_fvc_perc_pred_80",
  "pft_fev1_fvc_70",
  "pft_tlco",
  "pft_tlco_pred",
  "pft_tlco_pred_80",
  "pft_kco",           
  "pft_kco_pred",
  "pft_kco_pred_80",
  "bnp_summary",
  "hba1c_summary",
  "egfr_summary",
  "ddi_result",
  "ddi_summary",
  "crp_summary"
)
```


### Row proportions

```{r}
phosp_3m %>%
  left_join(phosp_wt_table) %>% 
  left_join(phosp_pft_table) %>% 
  left_join(phosp_bloods_table) %>% 
  left_join(phosp_hosp %>% select(study_id, crf1a_resp_support_4levels)) %>% 
  left_join(phosp_cluster) %>% 
  select(dependent, explanatory_hrqol) %T>% 
  {data_in <<- .} %>% 
  summary_factorlist(dependent,  explanatory_hrqol,
                     na_include = TRUE, 
                     total_col = TRUE, column = FALSE,  cont_nonpara = c(2),
                     add_col_totals = TRUE, add_row_totals = TRUE, include_row_missing_col = FALSE,
                     p = TRUE) %>%
  mytable()
```




### Column proportions

```{r}
phosp_3m %>%
  left_join(phosp_wt_table) %>% 
  left_join(phosp_pft_table) %>% 
  left_join(phosp_bloods_table) %>% 
  left_join(phosp_hosp %>% select(study_id, crf1a_resp_support_4levels)) %>% 
  left_join(phosp_cluster) %>% 
  select(dependent, explanatory_hrqol) %T>% 
  {data_in <<- .} %>% 
  summary_factorlist(dependent,  explanatory_hrqol,
                     na_include = TRUE, 
                     total_col = TRUE, column = TRUE, cont_nonpara = c(2),
                     add_col_totals = TRUE, add_row_totals = TRUE, include_row_missing_col = FALSE,
                     p = TRUE) %>%
  mytable()
```

## Table 4

### Row proportions
```{r}
explanatory_occupation = c(
  # "crf1b_healthcare_worker", "crf1b_caring",
  "social_status_before", #  "social_status_after", 
  "working_status_change", "working_less", 
  "no_longer_working", "health_reasons",
  "employer_reasons", "other_reasons"
  
  # "patient_sq_q", "patient_sq_q_today", "patient_sq_q_change",
  # "patient_sq_p_smoking", "patient_sq_p_drinking",
  # "patient_sq_p_eating", "patient_sq_p_activity"
)

phosp_3m %>%
  left_join(phosp_hosp %>% select(study_id, crf1a_resp_support_4levels, crf1b_healthcare_worker, crf1b_caring)) %>% 
  left_join(phosp_cluster) %>% 
  summary_factorlist(dependent,  explanatory_occupation,
                     na_include = TRUE, 
                     total_col = TRUE, column = FALSE, 
                     add_col_totals = TRUE, add_row_totals = TRUE, include_row_missing_col = FALSE,
                     p = TRUE) %>% 
  mytable()
```

### Column proportions

```{r}
phosp_3m %>%
  left_join(phosp_hosp %>% select(study_id, crf1a_resp_support_4levels, crf1b_healthcare_worker, crf1b_caring)) %>% 
  left_join(phosp_cluster) %>% 
  summary_factorlist(dependent,  explanatory_occupation,
                     na_include = TRUE, 
                     total_col = TRUE, column = TRUE, 
                     add_col_totals = TRUE, add_row_totals = TRUE, include_row_missing_col = FALSE,
                     p = TRUE) %>% 
  mytable()
```

## CRP vs BMI figure

```{r}
cor_result = phosp_3m %>% 
  left_join(phosp_bloods_table) %>% 
  left_join(phosp_cluster) %>% 
  select(crp_result, crf3a_bmi, cluster) %>% 
  filter(crf3a_bmi < 70) %$%
  cor.test(log(crp_result), crf3a_bmi) %>% 
  tidy()

cor_label = paste0("Pearson correlation coefficient\n", cor_result$estimate %>% round_tidy(3), " (p ", cor_result$p.value %>% p_tidy(3), ")")
```

```{r fig.height=6, fig.width=8}
p1 = phosp_3m %>% 
  left_join(phosp_bloods_table) %>% 
  left_join(phosp_cluster) %>% 
  select(crp_result, crf3a_bmi, cluster) %>% 
  filter(crf3a_bmi < 70) %>% 
  drop_na() %T>% 
  {total_n <<- dim(.)[[1]]} %>% 
  ggplot_lancet(aes(crf3a_bmi, crp_result, colour = cluster)) +
  geom_jitter(alpha = 0.5) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_colour_brewer("",palette = "Set1") +
  scale_y_log10() + 
  labs(x = "BMI", y = "CRP (mg/L, log scale)") +
  annotate("text", x = 60, y = 1, label = cor_label, hjust = 1) +
  guides(colour = guide_legend(ncol = 2)) +
  ggtitle("CRP by BMI",
          "Fitted line: linear regression")
p1
```

```{r}
phosp_3m %>% 
  left_join(phosp_bloods_table) %>% 
  left_join(phosp_cluster) %>% 
  select(crp_result, crf3a_bmi, cluster) %>% 
  filter(crf3a_bmi < 70) %$%
  cor.test(log(crp_result), crf3a_bmi)
```

```{r}
phosp_3m %>% 
  left_join(phosp_bloods_table) %>% 
  left_join(phosp_cluster) %>% 
  select(crp_result, crf3a_bmi, cluster) %>% 
  filter(crf3a_bmi < 70) %>% 
  lmmulti("log(crp_result)", c("crf3a_bmi")) %>% 
  summary()
```


```{r}
phosp_3m %>% 
  left_join(phosp_bloods_table) %>% 
  left_join(phosp_cluster) %>% 
  select(crp_result, crf3a_bmi, cluster) %>% 
  filter(crf3a_bmi < 70) %>% 
  lmmulti("log(crp_result)", c("crf3a_bmi", "cluster")) %>% 
  summary()
```

